### 2009-08-07 doc/latex/cowichan__tbb_2mandel_8cpp.tex
Re-generated doxygen with linuxtuples additions.

\hypertarget{cowichan__tbb_2life_8cpp}{
\section{cowichan\_\-tbb/life.cpp File Reference}
\label{cowichan__tbb_2life_8cpp}\index{cowichan\_\-tbb/life.cpp@{cowichan\_\-tbb/life.cpp}}
}
TBB life implementation.

{\tt \#include \char`\"{}cowichan\_\-tbb.hpp\char`\"{}}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classcowichan__tbb_1_1_game_of_life}{cowichan\_\-tbb::GameOfLife}
\begin{CompactList}\small\item\em Ping-pong solution to game of life. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__tbb}{cowichan\_\-tbb}
\begin{CompactList}\small\item\em Additional classes and functions specific to tbb implementation. \item\end{CompactList}

@@

\subsection{Detailed Description}
TBB life implementation.

\begin{Desc}
\item[See also:]\hyperlink{class_cowichan_t_b_b_273e3e8a2e05108f59ec613472bfa363}{CowichanTBB::life} \end{Desc}

>>>>

\hypertarget{cowichan__tbb_2mandel_8cpp}{
\section{cowichan\_\-tbb/mandel.cpp File Reference}
\label{cowichan__tbb_2mandel_8cpp}\index{cowichan\_\-tbb/mandel.cpp@{cowichan\_\-tbb/mandel.cpp}}
}
TBB mandel implementation.

{\tt \#include \char`\"{}cowichan\_\-tbb.hpp\char`\"{}}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classcowichan__tbb_1_1_mandelbrot}{cowichan\_\-tbb::Mandelbrot}
\begin{CompactList}\small\item\em Perform mandelbrot generation. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__tbb}{cowichan\_\-tbb}
\begin{CompactList}\small\item\em Additional classes and functions specific to tbb implementation. \item\end{CompactList}

@@

\subsection{Detailed Description}
TBB mandel implementation.

\begin{Desc}
\item[See also:]\hyperlink{class_cowichan_t_b_b_1e58b60ff22a58aba69567ecc6740878}{CowichanTBB::mandel} \end{Desc}

### 2009-08-07 doc/latex/cowichan__tbb_2product_8cpp.tex
Re-generated doxygen with linuxtuples additions.

\hypertarget{cowichan__tbb_2outer_8cpp}{
\section{cowichan\_\-tbb/outer.cpp File Reference}
\label{cowichan__tbb_2outer_8cpp}\index{cowichan\_\-tbb/outer.cpp@{cowichan\_\-tbb/outer.cpp}}
}
TBB outer implementation.

{\tt \#include \char`\"{}cowichan\_\-tbb.hpp\char`\"{}}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classcowichan__tbb_1_1_point_distances}{cowichan\_\-tbb::PointDistances}
\begin{CompactList}\small\item\em Fills in matrix and vector with distances. \item\end{CompactList}\item 
class \hyperlink{classcowichan__tbb_1_1_make_dominant}{cowichan\_\-tbb::MakeDominant}
\begin{CompactList}\small\item\em Makes a given matrix diagonally dominant. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__tbb}{cowichan\_\-tbb}
\begin{CompactList}\small\item\em Additional classes and functions specific to tbb implementation. \item\end{CompactList}

@@

\subsection{Detailed Description}
TBB outer implementation.

\begin{Desc}
\item[See also:]\hyperlink{class_cowichan_t_b_b_92a763b9733cdcceda13b7b7ea0bc229}{CowichanTBB::outer} \end{Desc}

>>>>

\hypertarget{cowichan__tbb_2product_8cpp}{
\section{cowichan\_\-tbb/product.cpp File Reference}
\label{cowichan__tbb_2product_8cpp}\index{cowichan\_\-tbb/product.cpp@{cowichan\_\-tbb/product.cpp}}
}
TBB product implementation.

{\tt \#include \char`\"{}cowichan\_\-tbb.hpp\char`\"{}}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classcowichan__tbb_1_1_product}{cowichan\_\-tbb::Product}
\begin{CompactList}\small\item\em Performs matrix vector product. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__tbb}{cowichan\_\-tbb}
\begin{CompactList}\small\item\em Additional classes and functions specific to tbb implementation. \item\end{CompactList}

@@

\subsection{Detailed Description}
TBB product implementation.

\begin{Desc}
\item[See also:]\hyperlink{class_cowichan_t_b_b_f3144458520e2dff1f9fad5753f6fc3d}{CowichanTBB::product} \end{Desc}

### 2009-08-07 doc/latex/cowichan__tbb_2randmat_8cpp.tex
Re-generated doxygen with linuxtuples additions.

\hypertarget{cowichan__tbb_2product_8cpp}{
\section{cowichan\_\-tbb/product.cpp File Reference}
\label{cowichan__tbb_2product_8cpp}\index{cowichan\_\-tbb/product.cpp@{cowichan\_\-tbb/product.cpp}}
}
TBB product implementation.

{\tt \#include \char`\"{}cowichan\_\-tbb.hpp\char`\"{}}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classcowichan__tbb_1_1_product}{cowichan\_\-tbb::Product}
\begin{CompactList}\small\item\em Performs matrix vector product. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__tbb}{cowichan\_\-tbb}
\begin{CompactList}\small\item\em Additional classes and functions specific to tbb implementation. \item\end{CompactList}

@@

\subsection{Detailed Description}
TBB product implementation.

\begin{Desc}
\item[See also:]\hyperlink{class_cowichan_t_b_b_f3144458520e2dff1f9fad5753f6fc3d}{CowichanTBB::product} \end{Desc}

>>>>

\hypertarget{cowichan__tbb_2randmat_8cpp}{
\section{cowichan\_\-tbb/randmat.cpp File Reference}
\label{cowichan__tbb_2randmat_8cpp}\index{cowichan\_\-tbb/randmat.cpp@{cowichan\_\-tbb/randmat.cpp}}
}
TBB randmat implementation.

{\tt \#include \char`\"{}cowichan\_\-tbb.hpp\char`\"{}}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classcowichan__tbb_1_1_random_generator}{cowichan\_\-tbb::RandomGenerator}
\begin{CompactList}\small\item\em Random generator. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__tbb}{cowichan\_\-tbb}
\begin{CompactList}\small\item\em Additional classes and functions specific to tbb implementation. \item\end{CompactList}

@@

\subsection{Detailed Description}
TBB randmat implementation.

\begin{Desc}
\item[See also:]\hyperlink{class_cowichan_t_b_b_b9b5cb4b4b5dc8907b2a01825cd4aaff}{CowichanTBB::randmat} \end{Desc}

### 2009-08-07 doc/latex/cowichan__tbb_2sor_8cpp.tex
Re-generated doxygen with linuxtuples additions.

\hypertarget{cowichan__tbb_2randmat_8cpp}{
\section{cowichan\_\-tbb/randmat.cpp File Reference}
\label{cowichan__tbb_2randmat_8cpp}\index{cowichan\_\-tbb/randmat.cpp@{cowichan\_\-tbb/randmat.cpp}}
}
TBB randmat implementation.

{\tt \#include \char`\"{}cowichan\_\-tbb.hpp\char`\"{}}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classcowichan__tbb_1_1_random_generator}{cowichan\_\-tbb::RandomGenerator}
\begin{CompactList}\small\item\em Random generator. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__tbb}{cowichan\_\-tbb}
\begin{CompactList}\small\item\em Additional classes and functions specific to tbb implementation. \item\end{CompactList}

@@

\subsection{Detailed Description}
TBB randmat implementation.

\begin{Desc}
\item[See also:]\hyperlink{class_cowichan_t_b_b_b9b5cb4b4b5dc8907b2a01825cd4aaff}{CowichanTBB::randmat} \end{Desc}

>>>>

\hypertarget{cowichan__tbb_2sor_8cpp}{
\section{cowichan\_\-tbb/sor.cpp File Reference}
\label{cowichan__tbb_2sor_8cpp}\index{cowichan\_\-tbb/sor.cpp@{cowichan\_\-tbb/sor.cpp}}
}
TBB sor implementation.

{\tt \#include \char`\"{}cowichan\_\-tbb.hpp\char`\"{}}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classcowichan__tbb_1_1_relaxer}{cowichan\_\-tbb::Relaxer}
\begin{CompactList}\small\item\em Performs one iteration of relaxation. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__tbb}{cowichan\_\-tbb}
\begin{CompactList}\small\item\em Additional classes and functions specific to tbb implementation. \item\end{CompactList}

@@

\subsection{Detailed Description}
TBB sor implementation.

\begin{Desc}
\item[See also:]\hyperlink{class_cowichan_t_b_b_dbb32ce457d0edca6815ab1cb2459276}{CowichanTBB::sor} \end{Desc}

### 2009-08-07 doc/latex/cowichan__tbb_2winnow_8cpp.tex
Re-generated doxygen with linuxtuples additions.

\hypertarget{cowichan__tbb_2vecdiff_8cpp}{
\section{cowichan\_\-tbb/vecdiff.cpp File Reference}
\label{cowichan__tbb_2vecdiff_8cpp}\index{cowichan\_\-tbb/vecdiff.cpp@{cowichan\_\-tbb/vecdiff.cpp}}
}
TBB vecdiff implementation.

{\tt \#include \char`\"{}cowichan\_\-tbb.hpp\char`\"{}}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classcowichan__tbb_1_1_norm_diff}{cowichan\_\-tbb::NormDiff}
\begin{CompactList}\small\item\em This class takes the 1-norm of the difference between two vectors. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__tbb}{cowichan\_\-tbb}
\begin{CompactList}\small\item\em Additional classes and functions specific to tbb implementation. \item\end{CompactList}

@@

\subsection{Detailed Description}
TBB vecdiff implementation.

\begin{Desc}
\item[See also:]\hyperlink{class_cowichan_t_b_b_28c976743df231fd183e4db9306050b1}{CowichanTBB::vecdiff} \end{Desc}

>>>>

\hypertarget{cowichan__tbb_2winnow_8cpp}{
\section{cowichan\_\-tbb/winnow.cpp File Reference}
\label{cowichan__tbb_2winnow_8cpp}\index{cowichan\_\-tbb/winnow.cpp@{cowichan\_\-tbb/winnow.cpp}}
}
TBB winnow implementation.

{\tt \#include \char`\"{}cowichan\_\-tbb.hpp\char`\"{}}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classcowichan__tbb_1_1_point_count}{cowichan\_\-tbb::PointCount}
\begin{CompactList}\small\item\em Calculates the number of points to sort for winnow. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__tbb}{cowichan\_\-tbb}
\begin{CompactList}\small\item\em Additional classes and functions specific to tbb implementation. \item\end{CompactList}

@@

\subsection{Detailed Description}
TBB winnow implementation.

\begin{Desc}
\item[See also:]\hyperlink{class_cowichan_t_b_b_77178470ef780e0505137dc1d22a85a2}{CowichanTBB::winnow} \end{Desc}

### 2009-08-07 doc/latex/files.tex
Re-generated doxygen with linuxtuples additions.

>>>>

\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_8cpp}{cowichan\_\-lt.cpp} (Entry point for the cowichan linuxtuples application )}{\pageref{cowichan__lt_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_8hpp}{cowichan\_\-lt.hpp} (Datatypes and common routines for \hyperlink{class_cowichan}{Cowichan} programs; LinuxTuples implementation )}{\pageref{cowichan__lt_8hpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_2src_2gauss_8cpp}{gauss.cpp} (LinuxTuples gauss implementation )}{\pageref{cowichan__lt_2src_2gauss_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{gauss_8hpp}{gauss.hpp} (LinuxTuples gauss header file )}{\pageref{gauss_8hpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_2src_2half_8cpp}{half.cpp} (LinuxTuples half implementation )}{\pageref{cowichan__lt_2src_2half_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{half_8hpp}{half.hpp} (LinuxTuples halving shuffle header file )}{\pageref{half_8hpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_2src_2hull_8cpp}{hull.cpp} (LinuxTuples hull implementation )}{\pageref{cowichan__lt_2src_2hull_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{hull_8hpp}{hull.hpp} (LinuxTuples iterative convex hull header file )}{\pageref{hull_8hpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_2src_2invperc_8cpp}{invperc.cpp} (LinuxTuples (actually serial) invperc implementation )}{\pageref{cowichan__lt_2src_2invperc_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_2src_2life_8cpp}{life.cpp} (LinuxTuples life implementation )}{\pageref{cowichan__lt_2src_2life_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{life_8hpp}{life.hpp} (LinuxTuples conway's game of life header file )}{\pageref{life_8hpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_2src_2mandel_8cpp}{mandel.cpp} (LinuxTuples mandelbrot set implementation )}{\pageref{cowichan__lt_2src_2mandel_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{mandel_8hpp}{mandel.hpp} (LinuxTuples mandelbrot set header file )}{\pageref{mandel_8hpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_2src_2norm_8cpp}{norm.cpp} (LinuxTuples norm implementation )}{\pageref{cowichan__lt_2src_2norm_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{norm_8hpp}{norm.hpp} (LinuxTuples norm header file )}{\pageref{norm_8hpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_2src_2outer_8cpp}{outer.cpp} (LinuxTuples outer implementation )}{\pageref{cowichan__lt_2src_2outer_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{outer_8hpp}{outer.hpp} (LinuxTuples outer product header file )}{\pageref{outer_8hpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_2src_2product_8cpp}{product.cpp} (LinuxTuples product implementation )}{\pageref{cowichan__lt_2src_2product_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{product_8hpp}{product.hpp} (LinuxTuples product header file )}{\pageref{product_8hpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_2src_2randmat_8cpp}{randmat.cpp} (LinuxTuples randmat implementation )}{\pageref{cowichan__lt_2src_2randmat_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{randmat_8hpp}{randmat.hpp} (LinuxTuples header file for the randmat cowichan problem )}{\pageref{randmat_8hpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_2src_2sor_8cpp}{sor.cpp} (LinuxTuples successive over-relaxation implementation )}{\pageref{cowichan__lt_2src_2sor_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{sor_8hpp}{sor.hpp} (LinuxTuples successive over-relaxation header file )}{\pageref{sor_8hpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_2src_2thresh_8cpp}{thresh.cpp} (LinuxTuples thresh implementation )}{\pageref{cowichan__lt_2src_2thresh_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{thresh_8hpp}{thresh.hpp} (LinuxTuples histogram thresholding header file )}{\pageref{thresh_8hpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{tuple__common_8cpp}{tuple\_\-common.cpp} (Implementation of common tuple application logic )}{\pageref{tuple__common_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{tuple__common_8hpp}{tuple\_\-common.hpp} (Header file for tuple applications )}{\pageref{tuple__common_8hpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_2src_2vecdiff_8cpp}{vecdiff.cpp} (LinuxTuples vecdiff implementation )}{\pageref{cowichan__lt_2src_2vecdiff_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{vecdiff_8hpp}{vecdiff.hpp} (LinuxTuples vector difference header file )}{\pageref{vecdiff_8hpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{cowichan__lt_2src_2winnow_8cpp}{winnow.cpp} (LinuxTuples winnow implementation )}{\pageref{cowichan__lt_2src_2winnow_8cpp}}{}
\item\contentsline{section}{cowichan\_\-lt/src/\hyperlink{winnow_8hpp}{winnow.hpp} (LinuxTuples winnow header file )}{\pageref{winnow_8hpp}}{}

### 2009-08-07 doc/latex/hierarchy.tex
doxygen documentation as of now
Re-generated doxygen with linuxtuples additions.

\section{Class Hierarchy}
This inheritance list is sorted roughly, but not completely, alphabetically:\begin{CompactList}
\item \contentsline{section}{Cowichan}{\pageref{class_cowichan}}{}
\begin{CompactList}
\item \contentsline{section}{CowichanOpenMP}{\pageref{class_cowichan_open_m_p}}{}
\item \contentsline{section}{CowichanSerial}{\pageref{class_cowichan_serial}}{}
\item \contentsline{section}{CowichanTBB}{\pageref{class_cowichan_t_b_b}}{}
\end{CompactList}
\item \contentsline{section}{cowichan\_\-tbb::GameOfLife}{\pageref{classcowichan__tbb_1_1_game_of_life}}{}
\item \contentsline{section}{cowichan\_\-tbb::Histogram}{\pageref{classcowichan__tbb_1_1_histogram}}{}
\item \contentsline{section}{cowichan\_\-tbb::MakeDominant}{\pageref{classcowichan__tbb_1_1_make_dominant}}{}
\item \contentsline{section}{cowichan\_\-tbb::Mandelbrot}{\pageref{classcowichan__tbb_1_1_mandelbrot}}{}
\item \contentsline{section}{cowichan\_\-tbb::MaximumDistance}{\pageref{classcowichan__tbb_1_1_maximum_distance}}{}
\item \contentsline{section}{cowichan\_\-tbb::MaxReducer}{\pageref{classcowichan__tbb_1_1_max_reducer}}{}
\item \contentsline{section}{cowichan\_\-tbb::MinMaxReducer}{\pageref{classcowichan__tbb_1_1_min_max_reducer}}{}
\item \contentsline{section}{cowichan\_\-tbb::Normalizer}{\pageref{classcowichan__tbb_1_1_normalizer}}{}
\item \contentsline{section}{cowichan\_\-tbb::NormDiff}{\pageref{classcowichan__tbb_1_1_norm_diff}}{}
\item \contentsline{section}{cowichan\_\-serial::PercPoint}{\pageref{classcowichan__serial_1_1_perc_point}}{}
\item \contentsline{section}{cowichan\_\-tbb::PercPoint}{\pageref{classcowichan__tbb_1_1_perc_point}}{}
\item \contentsline{section}{cowichan\_\-openmp::PercPoint}{\pageref{classcowichan__openmp_1_1_perc_point}}{}
\item \contentsline{section}{Point}{\pageref{class_point}}{}
\item \contentsline{section}{cowichan\_\-tbb::PointCount}{\pageref{classcowichan__tbb_1_1_point_count}}{}
\item \contentsline{section}{cowichan\_\-tbb::PointDistances}{\pageref{classcowichan__tbb_1_1_point_distances}}{}
\item \contentsline{section}{cowichan\_\-tbb::Product}{\pageref{classcowichan__tbb_1_1_product}}{}
\item \contentsline{section}{cowichan\_\-tbb::RandomGenerator}{\pageref{classcowichan__tbb_1_1_random_generator}}{}
\item \contentsline{section}{cowichan\_\-tbb::Relaxer}{\pageref{classcowichan__tbb_1_1_relaxer}}{}
\item \contentsline{section}{cowichan\_\-tbb::RowElimination}{\pageref{classcowichan__tbb_1_1_row_elimination}}{}
\item \contentsline{section}{cowichan\_\-tbb::Shuffle}{\pageref{classcowichan__tbb_1_1_shuffle}}{}
\item \contentsline{section}{cowichan\_\-tbb::Threshold}{\pageref{classcowichan__tbb_1_1_threshold}}{}
\item \contentsline{section}{WeightedPoint}{\pageref{class_weighted_point}}{}
\end{CompactList}

>>>>

\section{Class Hierarchy}
This inheritance list is sorted roughly, but not completely, alphabetically:\begin{CompactList}
\item \contentsline{section}{Cowichan}{\pageref{class_cowichan}}{}
\begin{CompactList}
\item \contentsline{section}{CowichanLinuxTuples}{\pageref{class_cowichan_linux_tuples}}{}
\item \contentsline{section}{CowichanMPI}{\pageref{class_cowichan_m_p_i}}{}
\item \contentsline{section}{CowichanOpenMP}{\pageref{class_cowichan_open_m_p}}{}
\item \contentsline{section}{CowichanSerial}{\pageref{class_cowichan_serial}}{}
\item \contentsline{section}{CowichanTBB}{\pageref{class_cowichan_t_b_b}}{}
\end{CompactList}
\item \contentsline{section}{cowichan\_\-tbb::GameOfLife}{\pageref{classcowichan__tbb_1_1_game_of_life}}{}
\item \contentsline{section}{cowichan\_\-tbb::Histogram}{\pageref{classcowichan__tbb_1_1_histogram}}{}
\item \contentsline{section}{cowichan\_\-tbb::MakeDominant}{\pageref{classcowichan__tbb_1_1_make_dominant}}{}
\item \contentsline{section}{cowichan\_\-tbb::Mandelbrot}{\pageref{classcowichan__tbb_1_1_mandelbrot}}{}
\item \contentsline{section}{cowichan\_\-tbb::MaximumDistance}{\pageref{classcowichan__tbb_1_1_maximum_distance}}{}
\item \contentsline{section}{cowichan\_\-tbb::MaxReducer}{\pageref{classcowichan__tbb_1_1_max_reducer}}{}
\item \contentsline{section}{cowichan\_\-tbb::MinMaxReducer}{\pageref{classcowichan__tbb_1_1_min_max_reducer}}{}
\item \contentsline{section}{cowichan\_\-tbb::Normalizer}{\pageref{classcowichan__tbb_1_1_normalizer}}{}
\item \contentsline{section}{cowichan\_\-tbb::NormDiff}{\pageref{classcowichan__tbb_1_1_norm_diff}}{}
\item \contentsline{section}{PercPoint}{\pageref{class_perc_point}}{}
\item \contentsline{section}{cowichan\_\-openmp::PercPoint}{\pageref{classcowichan__openmp_1_1_perc_point}}{}
\item \contentsline{section}{cowichan\_\-tbb::PercPoint}{\pageref{classcowichan__tbb_1_1_perc_point}}{}
\item \contentsline{section}{cowichan\_\-serial::PercPoint}{\pageref{classcowichan__serial_1_1_perc_point}}{}
\item \contentsline{section}{Point}{\pageref{class_point}}{}
\item \contentsline{section}{cowichan\_\-tbb::PointCount}{\pageref{classcowichan__tbb_1_1_point_count}}{}
\item \contentsline{section}{cowichan\_\-tbb::PointDistances}{\pageref{classcowichan__tbb_1_1_point_distances}}{}
\item \contentsline{section}{cowichan\_\-tbb::Product}{\pageref{classcowichan__tbb_1_1_product}}{}
\item \contentsline{section}{cowichan\_\-tbb::RandomGenerator}{\pageref{classcowichan__tbb_1_1_random_generator}}{}
\item \contentsline{section}{cowichan\_\-tbb::Relaxer}{\pageref{classcowichan__tbb_1_1_relaxer}}{}
\item \contentsline{section}{cowichan\_\-tbb::RowElimination}{\pageref{classcowichan__tbb_1_1_row_elimination}}{}
\item \contentsline{section}{cowichan\_\-tbb::Shuffle}{\pageref{classcowichan__tbb_1_1_shuffle}}{}
\item \contentsline{section}{cowichan\_\-tbb::Threshold}{\pageref{classcowichan__tbb_1_1_threshold}}{}
\item \contentsline{section}{TupleApplication}{\pageref{class_tuple_application}}{}
\begin{CompactList}
\item \contentsline{section}{LTBounds}{\pageref{class_l_t_bounds}}{}
\item \contentsline{section}{LTForward}{\pageref{class_l_t_forward}}{}
\item \contentsline{section}{LTFrequency}{\pageref{class_l_t_frequency}}{}
\item \contentsline{section}{LTHalf}{\pageref{class_l_t_half}}{}
\item \contentsline{section}{LTHull}{\pageref{class_l_t_hull}}{}
\item \contentsline{section}{LTLife}{\pageref{class_l_t_life}}{}
\item \contentsline{section}{LTMandel}{\pageref{class_l_t_mandel}}{}
\item \contentsline{section}{LTNorm}{\pageref{class_l_t_norm}}{}
\item \contentsline{section}{LTOuter}{\pageref{class_l_t_outer}}{}
\item \contentsline{section}{LTProduct}{\pageref{class_l_t_product}}{}
\item \contentsline{section}{LTRandmat}{\pageref{class_l_t_randmat}}{}
\item \contentsline{section}{LTSor}{\pageref{class_l_t_sor}}{}
\item \contentsline{section}{LTThresh}{\pageref{class_l_t_thresh}}{}
\item \contentsline{section}{LTVecdiff}{\pageref{class_l_t_vecdiff}}{}
\item \contentsline{section}{LTWinnow}{\pageref{class_l_t_winnow}}{}
\end{CompactList}
\item \contentsline{section}{WeightedPoint}{\pageref{class_weighted_point}}{}
\end{CompactList}
